---
output: 
   pdf_document:
      latex_engine: xelatex
header-includes:
# -----------------------------------
# LaTex Preamble
# specificy packages and options
# primary aesthetics
- \usepackage{geometry} 
- \usepackage{pdflscape, lscape}
- \usepackage{parskip}
- \usepackage{tocloft}

# Headers + Footers
- \usepackage{fancyhdr}
- \usepackage{lastpage}

# fonts
- \usepackage{fontspec}
#- \setmainfont{Avenir Next Ultra Light}
- \usepackage{anyfontsize}
- \usepackage{sectsty}

# references & TOC
- \usepackage{hyperref}
- \usepackage{tocloft}

# tables
- \usepackage{tikz}
- \usepackage{array}
- \usepackage{booktabs}
- \usepackage{tabularx}
- \usepackage{array}
- \usepackage{rotating}
- \usepackage{multirow}

# graphics
- \usepackage{graphicx}
- \usepackage{caption}

# colors and themes
- \usepackage{colortbl,xcolor, color}
- \definecolor{Darkgreen}{rgb}{0,0.4,0}
- \definecolor{LightBlue}{RGB}{222,235,247}
- \definecolor{LightGreen}{RGB}{229,245,224}
- \definecolor{LightOrange}{RGB}{254,230,206}

# -----------------------------------
# finish YAML
geometry: margin=0.75in
fontsize: 12pt
# do not add title, custom one below
---

<!--- ESTABLISH MAIN DOCUMENT PARAMETERS --->
``` {r echo = FALSE, label = "Title"}
# create custom header
title <- "shinyMaker Documentation"
title <- toupper(title)
date <- format(Sys.Date(),format = "%A %B %d, %Y") # format date
footdate <- format(Sys.Date(),format  = "%D")

# define latex controls
body.text.fs <- 12 # main body text size
document.vspace.default <- paste0(0.25,"cm") # vspace
document.vspace.title <- paste0(0.15,"cm") # vspace for space between title and document body
section.mainheaders.fs <- 16 # section headers size
section.subheaders.fs <- 14 # subsection header
title.date.fs <- 14 # main title date size
title.name.fs <- 21 # main title name size

# \rule{\textwidth}{0.25pt} # to add a horizontal line across document within margins
````

<!--- Define hyperlink aesthetics --->
\hypersetup{%
    pdfborder = {0 0 0},
    colorlinks,
    citecolor=red,
    filecolor=blue,
    linkcolor=black,
    urlcolor=Darkgreen
}

<!--- Define Headers and Footers --->
\fancypagestyle{plain}{%
  \renewcommand{\headrulewidth}{0pt}%
  \fancyhf{}%
  \fancyfoot[L]{\footnotesize `r footdate`}%
  \fancyfoot[C]{\footnotesize shinyMaker}%
  \fancyfoot[R]{\footnotesize Page \thepage\, of\, \pageref*{LastPage}}%
}

<!--- First page has no header or footers --->
\pagestyle{plain}

<!--- Create custom section header --->
\sectionfont{\fontsize{`r section.mainheaders.fs`}{10}\selectfont\sectabx}

\newcommand{\sectabx}[1]{%
\noindent\begin{tabularx}{\textwidth}{@{} l X @{} }
    \multirow{2}{*}{#1} & \\
    \cline{2-2}
    & \\
\end{tabularx}}

<!--- Make Header --->
\begin{center}
   \fontsize{`r title.name.fs`}{10}\selectfont `r title` \break
   \break
   \fontsize{`r title.date.fs`}{10}\selectfont `r date` \break
\end{center}

This document was written by \href{http://www.davidcruvolo.com}{David Ruvolo}.

\section{Introduction}

The shiny_maker.R script is a standard builder for creating Shiny apps.
Generating and setting up initial shiny files (i.e., server, ui, global, css, external, assets,
etc.) can be tedious and take a while to setup. In the first instance, this script
will generate navbarPages with default starter text. 

This function generates a shiny navbarPage and all necessary files. The app structure looks like this:

```{r eval = F, echo = T}
## directory structure
ShinyApp/
        --- global.R
        --- ui.R
        --- server.R
        --- data/
        --- external/
                    | --- main.R
        --- utilities/
                    | --- google-analytics.js
        --- www/
                    | --- style.css
```


\section{Usage}

The shiny_maker.R file has 3 functions built in.

###1. <code>%+=%<code>

The function <code>%+=%<code> is increments the left argument by a value on the right. This was 
implemented from \href{https://stackoverflow.com/questions/5738831/r-plus-equals-and-plus-plus-equivalent-from-c-c-java-etc}{this stackoverflow post}. 

```{r eval=T, echo = T}
`%+=%` = function(e1,e2) eval.parent(substitute(e1 <- e1 + e2))
x = 10
x %+=% 10
x
```

###2. navbarMaker()

The <code>navbarMaker()</code> is the first shiny app maker in the shinyMaker series. 

#### Parameters

The function <code>navbarMaker()</code> takes the follow parameters:

\begin{itemize}
    \item directory{\_}name: The name of the shiny app directory.
    \item dir{\_}path: The path for where you want the app stored. Default is desktop.
\end{itemize}

#### Examples

```{r eval = F, echo = T}

# source file
source("shiny_maker.R")

# basic usage
navbarMaker()

# specifying app name
navbarMaker(directory_name = "Project Analysis Tool")

# setting directory path
navbarMaker(dir_path = ".../Documents/")

# both options
navbarMaker(directory_name = "Visualization Tool", dir_path = ".../Documents")

```

###3. make_my_text_shiny()

The <code>make_my_text_shiny()</code> writes default text to the shiny app files.
Ships with navbarMaker() and reads the dir_path

```{r eval = F, echo = T}
make_my_text_shiny(file_path, file_type)
```
#### Parameters

The function <code>make_my_text_shiny()</code> takes the follow parameters:

\begin{itemize}
    \item file{\_}path: path of the file.
    \item file{\_}type: name the file type you are writing text to. Options include: ui, server, global, main, and css.
\end{itemize}

#### Examples

```{r echo = T, eval = F}

# source file
source("shiny_maker.R")

# write ui
make_my_text_shiny(file_path = "/path/to/dir/ui.R", file_type = "ui")

# write server
make_my_text_shiny(file_path = "/path/to/dir/ui.R", file_type = "server")

# write global
make_my_text_shiny(file_path = "/path/to/dir/ui.R", file_type = "global")

# write main tab Panel
make_my_text_shiny(file_path = "/path/to/dir/ui.R", file_type = "main")

# write css
make_my_text_shiny(file_path = "/path/to/dir/ui.R", file_type = "css")

```




